\documentclass{article}
\usepackage{../fasy-hw}

%% UPDATE these variables:
\renewcommand{\hwnum}{3}
\title{Discrete Structures, Homework \hwnum}
\author{Patrick O'Connor (Patrick OConnor (322))}
\collab{n/a}
\date{due: 19 February 2021}

\begin{document}

\maketitle

This homework assignment should be
submitted as a single PDF file both to D2L and to Gradescope.

General homework expectations:
\begin{itemize}
    \item Homework should be typeset using LaTex.
    \item Answers should be in complete sentences and proofread.
    \item You will not plagiarize.  \item List collaborators at the start of
    each question using the \texttt{collab} command.
    \item Put your answers where the \texttt{todo} command currently is (and
        remove the \texttt{todo}, but not the word \texttt{Answer}).
\end{itemize}

% ============================================
% ============================================
\collab{n/a} \nextprob{Negations}
% ============================================
% ============================================
Negate the following statements:

\begin{enumerate}

    \item Each ``Clean 'Cat Kit''  contains a cloth mask and a refillable hand
        sanitizer.

        \paragraph{Answer}
        There exists a `Clean 'Cat Kit'' that does not contain a cloth mask
        and a refillable hand
        sanitizer.

    \item There exists a boat docked in New Jersey that I have steered.

        \paragraph{Answer}
        I have not steered any of the boats docked in New Jersey.

    \item There exists an island in the Ohio River with a bowling alley and a
        university track field.

        \paragraph{Answer}
        On the Ohio River there is not an island with a bowling alley and
        university track field.

    \item Both my sister and I can climb every route at Spire.

        \paragraph{Answer}
        There exists a route at Spire that my sister and I can not climb

\end{enumerate}

% ============================================
% ============================================
\collab{n/a} \nextprob{Definitions}
% ============================================
% ============================================
Use the definitions provided in the course textbook to prove that every prime
number except~$2$ is odd.

\paragraph{Answer}

  Let $P \in \Z$
  $\forall$ r, s $\in \Z$
  if $P = rs$, then ($r=1 \land s=p$)$\lor$($s=1 \land r=P$)
  Let p $\in \Z$
  By definition of a prime number,
  $\forall$ p $p\mod{n} = 0$ if $n=p$
  Therefore, p is odd.


%
% ============================================
% ============================================
\collab{n/a}
\nextprob{Four Colors Suffice}
% ============================================
% ============================================
Read Chapters $2$ and $3$ of \emph{Four Colors Suffice} and answer the following
 questions:

\begin{enumerate}

    \item Who are the Austrian(s) mentioned in Chapters $1$--$3$, and what was
    their contribution mentioned in the book?

        \paragraph{Answer}
        The Austrian mentioned in Chapter $2$ is Heinrich Tietze. Teitze
        described a situation in which more than four colors are necessary in
        for three-dimensional maps. This situation involves taking a number of
        horizontal bars numbers 1 to n, that have vertical bars also
        numbered 1 to n. These are joined as a single country  if horizontal
        and vertical numbers match.
        This is similar to jenga blocks in a pile or legos blocks.
        After joining into countries, we have n three dimensional countries
         that are all touching each other.
        Therefore we would need n colors which if n is greater than ,
        the four color theorem does not apply.

    \item Write a statement of the four color theorem using a universal
        quantifier.

        \paragraph{Answer}
        For each map $m$, there are four colors needed to color it such that
        no same color comes into contact at more than a point.

    \item What is the definition of a $k$-coloring of a graph?

        \paragraph{Answer}
        To $k$-color a graph is to color the graph in less than or equal to
        $k$ colors. $colors\leq \ k$

    \item Prove or disprove: all planar graphs are three-colorable.

        \paragraph{Answer}
        \todo{}

    \item Assuming the four color theorem holds, prove or disprove: six colors
        suffice to color a plane graph.

        \paragraph{Answer}
        \todo{}

    \item Give an example of a map with at least five faces that has a
        two-coloring.  Be sure to provide a coloring as evidence that the map is
        two-colorable.

        \paragraph{Answer}
        \todo{your answer here.}

    \item Euler's formula states that if we have a map on the sphere or plane
        and count the exterior face as a face, then F-E+V=2.  Does this equation
        hold if the map is drawn on a M\"obius band? Why or why not? (Note:
        here, the boundary of the M\"obius band must be represented in the graph
        defining the map, and no ``country'' can be on the same side of a single
        edge.)

        \paragraph{Answer}
        \todo{your answer here.}

    \item In your own words, explain the joke: ``A topologist cannot tell the
        difference between a coffee cup and a donut.''  You are encouraged to
        use Wikipedia to formulate your answer, but be sure to cite sources.

        \paragraph{Answer}
        \todo{your answer here.}

\end{enumerate}

% ============================================
% ============================================
\collab{n/a}
\nextprob{Ada Lovelace}
% ============================================
% ============================================

Write a short (1-2 paragraph) biography of Ada Lovelace.
\textbf{In your own words}, describe who they are and why they are important in
the history of computer science.  If you use external resources, please provide
proper citations (see the `hw/bib-ex` folder for examples of how to use
citations). If you do not use external sources, please write ``I did not
use any sources to write this biography'' as the last sentence of the
\paragraph{Answer}

Ada Lovelace was an English mathematician during the early 1800's.
Ada Lovelace was a highly educated human who came from fame and fortune.
Her father was a famed poet Lord Byron, who is known for his romantic and
satirist poetry that represented Europe's imagination. Although this fame
most likely assisted in affording the private tutoring, Lord Byron left Britain
before Ana ever met him. She was privately educated by Augustus De Morgan who
you may know from De Morgan's laws which states that mathematical statements
and concepts are related through their oppositions/opposites.
After marrying into royalty in the 1830's, she pursued understanding and
progressing the pursuit of early computing that had been started
by Charles Babbage.

Within her work on Charles Babbage's proposed computer, the Analytical Engine,
she explored the ability for the Analytical Engine to follow a series of steps.
These steps would in today's language would be considered a program.
Her discovery of the ability for the Analytical Engine to follow steps was
found when translating and annotating an article written by Luigi Federico
Menabrea. Her deep understanding of the Analytical Engine assisted in writing
detailed annotations on how the computing device could calculate Bernoulli
numbers. At this point the detailed annotations were not system instructions
but rather an algorithm that stepped through instructions.
Along with defining what some would say is the first program,
she devised a vision for computers to be used as tools to interact
with other types of data such as words.


% %% ... the bibliography
% \newpage
% \bibliographystyle{acm}
% \bibliography{biblio}

\end{document}
